### 2014-09-19 LaTeX/RhodiumTheory.tex
Added more citations to take up space.

\cite{glaeser:shapiro:2001} discuss the historic role of cities in warfare and their current role with respect to terrorism. Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population. However, as the tactics of warfare have shifted over the centuries, the relationship between violent conflict and cities has become more complex. Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action. Finally, the authors point out that warfare destroys transportation infrastructure which can interfere both with commerce and with rebuilding during a conflict.

That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies. \cite[p. 137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the national state in economic analysis \citep{jacobs:1969,jacobs:1984}.  In the past three decades, economists have begun

@@

We turn now to an empirical test of our proposition.  Using a dataset that includes 510 years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.

>>>>

\cite{glaeser:shapiro:2002} discuss the historic role of cities in warfare and their current role with respect to terrorism. Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population. However, as the tactics of warfare have shifted over the centuries, the relationship between violent conflict and cities has become more complex. Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action. Finally, the authors point out that warfare destroys transportation infrastructure which can interfere both with commerce and with rebuilding during a conflict.

That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies. \cite[p. 137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.  In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}.

We extend this line of research by conceptualizing civil wars not as homogeneous national phenomenon, but as a diverse class of violent conflict with properties that distinguish the effects of one conflict from another. Since urban economies are responsible for a disproportionate share of national economic performance, civil conflicts in or near these engines of commerce should likewise exert a disproportionate influence on state performance.

@@

We turn now to an empirical test of our proposition.  Using a dataset that includes 510 country-years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
